---
pdf_document:
  toc: true
author: "Justin Yang"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: pdf_document
toc_depth: 3
toc_float:
  collapsed: false
title: "cogsci_results"
---

# Setup

```{r setup, include=F, message=F, warning=F}
# Function to automatically install and load packages
install_and_load <- function(packages) {
  options(repos = c(CRAN = "https://cloud.r-project.org/"))
  for (pkg in packages) {
    if (!require(pkg, character.only = TRUE)) {
      message(paste("Installing", pkg, "package..."))
      install.packages(pkg, dependencies = TRUE)
      
      if (!require(pkg, character.only = TRUE)) {
        stop(paste("Package", pkg, "could not be installed or loaded."))
      }
    }
    library(pkg, character.only = TRUE)
  }
}


required_packages <- c(
  "knitr", "ggstatsplot", "lme4", "lmerTest", "DT", "brms", "Metrics",
  "Hmisc", "xtable", "scales", "lemon", "ggplotify", "showtext", 
  "broom.mixed", "ggrepel", "patchwork", "png", "grid", "egg", 
  "ggtext", "bayesplot", "emmeans", "tidyverse"
)

install_and_load(required_packages)

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# Set default plot theme
theme_set(theme_classic() + theme(text = element_text(size = 14)))

set.seed(1)

# Directories
project_dir <- normalizePath(file.path(getwd(), "..", ".."))
data_dir_s1 <- file.path(project_dir, "data", "s1_quicksand")
data_dir_s2 <- file.path(project_dir, "data", "s2_quicksand")
figures_dir <- file.path(project_dir, "figures", "results")

cache_dir <- file.path(getwd(), "cache")
if (!dir.exists(cache_dir)) {
  dir.create(cache_dir)
}

# Optional: Force brms to refit models
# options(brms.file_refit = "always")

```

```{r}
# set style
condition_palette = c(
  "experience" = "#899CA5",
  "experience + hypothetical" = '#2B7CA1',
  "experience + counterfactual" = "#C04225"
  )

trial_palette = c(
    "navigation" = "#899CA5",
    "experience" = "#899CA5",
    "hypothetical" = '#2B7CA1',
    "counterfactual" = "#C04225"
  )

# only do if user if me (justyang) as its a custom font
if (Sys.info()['user'] == 'justyang') {
  font_add("AkzidenzGrotesk", "/Users/justyang/Library/Fonts/AkzidenzGroteskBE-Regular.otf")
  showtext_auto()
  
  theme_set(theme_classic(base_size = 14))
  theme_update(
    text = element_text(family = "AkzidenzGrotesk"),
    plot.title = element_text(family = "AkzidenzGrotesk"),
    axis.text = element_text(family = "AkzidenzGrotesk"),
    axis.title = element_text(family = "AkzidenzGrotesk"),
    legend.text = element_text(family = "AkzidenzGrotesk"),
    legend.title = element_text(family = "AkzidenzGrotesk"),
    plot.tag = element_text(family = "AkzidenzGrotesk")
  )
}
```

```{r}
# load data
session_df_s1 = read_csv(file.path(data_dir_s1, 'session_data.csv'))
world_df_s1 = read_csv(file.path(data_dir_s1, 'world_data.csv'))
quicksand_df_s1 = read_csv(file.path(data_dir_s1, 'trial_data.csv'))
model_df_s1 = read_csv(file.path(data_dir_s1, 'model_predictions.csv'))

session_df_s2 = read_csv(file.path(data_dir_s2, 'session_data.csv'))
world_df_s2 = read_csv(file.path(data_dir_s2, 'world_data.csv'))
quicksand_df_s2 = read_csv(file.path(data_dir_s2, 'trial_data.csv'))
model_df_s2 = read_csv(file.path(data_dir_s2, 'model_predictions.csv'))


bins = 3
day_labels = paste0("split ", 1:bins, " of ", bins)

quicksand_df_s1 <- quicksand_df_s1 %>%
  mutate(days_binned = cut_number(day, bins, labels = day_labels))
quicksand_df_s2 <- quicksand_df_s2 %>%
  mutate(days_binned = cut_number(day, bins, labels = day_labels))

quicksand_df_s1 <- quicksand_df_s1 %>% 
  mutate(condition = factor(condition, levels = c("observation", "hypothetical", "counterfactual")))
quicksand_df_s2 <- quicksand_df_s2 %>% 
  mutate(condition = factor(condition, levels = c("observation", "hypothetical", "counterfactual")))  

quicksand_df_s2 <- quicksand_df_s2 %>%
  mutate(trial_type = recode(
    trial_type,
    "quicksand-planner" = "navigation",
    "quicksand-simulate" = "counterfactual"
  ))
```

# Analysis

## Study 1 results

### Simulation path performance

**Are counterfactual paths safer than hypothetical paths?**

```{r}
fit.s1_manipulation_check = quicksand_df_s1 %>% 
  left_join(world_df_s1 %>% select(world_id, world_spec_id), by = "world_id") %>%
  rename(environment = world_spec_id) %>% 
  filter(condition %in% c('hypothetical', 'counterfactual'),
         trial_type == 'quicksand-simulate') %>%
  mutate(counterfactual = as.numeric(condition == 'counterfactual')) %>% 
  brm(
    formula = hazard_count ~ 1 + counterfactual + (1 + counterfactual | game_id) + (1 | environment),
    family = poisson(),
    seed = 1,
    cores = parallel::detectCores(),
    file = 'cache/fit.s1_manipulation_check'
  )

summary(fit.s1_manipulation_check)

fit.s1_manipulation_check %>% 
  emmeans(specs=pairwise~counterfactual)

posterior <- as_draws_df(fit.s1_manipulation_check)
mcmc_areas(posterior, 
           pars = c("b_Intercept", "b_counterfactual"),
           prob = 0.95) +  # Show 95% credible intervals
  ggtitle("Posterior Distributions of Coefficients") +
  xlab("Estimate")
```

### Hypothesis 1: Counterfactual simulation produces safer paths than the other conditions

```{r}
fit.s1_hypothesis1 = quicksand_df_s1 %>% 
  left_join(world_df_s1 %>% select(world_id, world_spec_id), by = "world_id") %>%
  rename(environment = world_spec_id) %>% 
  filter(trial_type == 'quicksand-planner') %>%
  mutate(condition = factor(condition, levels = c("observation", "hypothetical", "counterfactual"))) %>%
  brm(
    formula = hazard_count ~ 1 + condition * day + (1 + day | game_id) + (1 | environment),
    family = poisson(),
    seed = 1,
    chains = 8,
    iter = 4000,
    cores = parallel::detectCores(),
    file = 'cache/fit.s1_hypothesis1'
  )

summary(fit.s1_hypothesis1)

fit.s1_hypothesis1 %>% # in non-log scale
  emmeans(specs = pairwise~condition) 
  
fit.s1_hypothesis1 %>% # in non-log scale
  emtrends(specs = pairwise~condition, var = "day") 

posterior <- as_draws_df(fit.s1_hypothesis1)
mcmc_areas(posterior, 
           regex_pars = "b_condition",
           prob = 0.95) +  # Show 95% credible intervals
  ggtitle("Posterior Distributions of Coefficients") +
  xlab("Estimate")

```

### Counterfactual vs. Hypothetical condition

```{r}
fit.s1_hypothetical = quicksand_df_s1 %>% 
  left_join(world_df_s1 %>% select(world_id, world_spec_id), by = "world_id") %>%
  rename(environment = world_spec_id) %>% 
  filter(
    (trial_type == 'quicksand-planner') & (condition %in% c("hypothetical", "counterfactual"))) %>%
  mutate(condition = factor(condition, levels = c("hypothetical", "counterfactual"))) %>%
  brm(
    formula = hazard_count ~ 1 + condition * day + (1 + day | game_id) + (1 | environment),
    family = poisson(),
    seed = 1,
    chains = 8,
    iter = 4000,
    cores = parallel::detectCores(),
    file = 'cache/fit.s1_hypothetical'
  )

summary(fit.s1_hypothetical)

fit.s1_hypothetical %>%
  emmeans(specs = pairwise~condition)

fit.s1_hypothetical %>%
  emtrends(specs = pairwise~condition, var = "day")

```

## Study 2 results

We follow the analysis plan outlined in the preregistration: <https://osf.io/tzha7>.

### Manipulation checks

**Do people understand what to do when simulating counterfactuals?**

In counterfactual simulation trials, participants make paths from start to goal, conditioning on the outcome of their previous experience. With the task of improving on their previous plan, we should expect that participants’ counterfactual paths should at minimum be as good as their previous path, as that would simply amount to retracing their previous steps. So we test participants’ understanding or engagement of the counterfactual trials by first asking if participants’ counterfactual paths outperform their actual paths by fitting a Bayesian mixed-effects model on the number of unsafe tiles in a path between matched actual and counterfactual paths:

```         
hazard_count ~ 1 + counterfactual + (1 + counterfactual | participant) + (1 | environment)
```

Here we encode for each trial, the number of unsafe tiles on the actual path (counterfactual = 0) and the number of unsafe tiles on the counterfactual path (counterfactual = 1). We expect the mean posterior distribution on the parameter for “counterfactual” to be negative, and that the 95% credible interval of that distribution excludes 0. For this and all future analyses that model the number of unsafe tiles in a path, we will assume a Poisson distribution.

```{r}
fit.s2_manipulation_check = quicksand_df_s2 %>% 
  left_join(world_df_s2 %>% select(world_id, world_spec_id), by = "world_id") %>%
  rename(environment = world_spec_id) %>% 
  filter(condition == 'counterfactual') %>%
  mutate(counterfactual = as.numeric(trial_type == 'counterfactual')) %>% 
  brm(
    formula = hazard_count ~ 1 + counterfactual + (1 + counterfactual | game_id) + (1 | environment),
    family = poisson(),
    seed = 1,
    cores = parallel::detectCores(),
    file = 'cache/fit.s2_manipulation_check'
  )

summary(fit.s2_manipulation_check)

fit.s2_manipulation_check %>% 
  emmeans(specs=pairwise~counterfactual)

posterior <- as_draws_df(fit.s2_manipulation_check)
mcmc_areas(posterior, 
           pars = c("b_Intercept", "b_counterfactual"),
           prob = 0.95) +  # Show 95% credible intervals
  ggtitle("Posterior Distributions of Coefficients") +
  xlab("Estimate")

```

### Hypothesis 1: Counterfactual simulation produces safer paths

Does engaging in counterfactual simulation result in fewer encounters with hazards when navigating a gridworld environment? Our analysis will consist of understanding whether participants assigned to the counterfactual condition encounter fewer hazards on navigation trials, for which we use the following Bayesian mixed-effects model structure (using a Poisson distribution):

```{r}
fit.s2_hypothesis1 = quicksand_df_s2 %>% 
  left_join(world_df_s2 %>% select(world_id, world_spec_id), by = "world_id") %>%
  rename(environment = world_spec_id) %>% 
  filter(trial_type == 'navigation') %>%
  mutate(condition = ifelse(condition == "counterfactual", 1, -1),) %>% 
  brm(
    formula = hazard_count ~ 1 + condition * day + (1 + day | game_id) + (1 | environment),
    family = poisson(),
    seed = 1,
    chains = 8,
    iter = 4000,
    cores = parallel::detectCores(),
    file = 'cache/fit.s2_hypothesis1'
  )

summary(fit.s2_hypothesis1)

fit.s2_hypothesis1 %>%
  emmeans(specs=pairwise~condition)


fit.s2_hypothesis1 %>%
  emtrends(specs = pairwise~condition, var = "day")

posterior <- as_draws_df(fit.s2_hypothesis1)
mcmc_areas(posterior, 
           pars = c("b_condition", "b_day", "b_condition:day"),
           prob = 0.95) +  # Show 95% credible intervals
  ggtitle("Posterior Distributions of Coefficients") +
  xlab("Estimate")

```


### Hypothesis 2: Counterfactual simulation produces a more accurate mental model of the environment

Our primary analysis in this experiment focuses on whether participants’ ability to reason counterfactually could result in a greater understanding of their environment. We operationalize this notion of understanding in an exam trial where participants mark which tiles they think are safe or unsafe in their gridworld environment.

#### Hypothesis 2a: Exam accuracy

We compare the accuracies of the responses in the exam trials across the observation and counterfactual conditions. We predict that responses in the counterfactual condition will be more accurate than those in the observational condition.

```{r}
fit.s2_hypothesis2a = world_df_s2 %>% 
  rename(environment = world_spec_id) %>% 
  mutate(condition = ifelse(condition == "counterfactual", 1, -1)) %>% 
  brm(
    formula = exam_trial_correct_tiles ~ 1 + condition + (1 | game_id) + (1 | environment),
    seed = 1,
    chains = 8,
    iter = 4000,
    cores = parallel::detectCores(),
    file = 'cache/fit.s2_hypothesis2a'
  )

summary(fit.s2_hypothesis2a)

fit.s2_hypothesis2a %>%
  emmeans(specs=pairwise~condition)

posterior <- as_draws_df(fit.s2_hypothesis2a)
mcmc_areas(posterior, 
           pars = c("b_Intercept", "b_condition"),
           prob = 0.95) +  # Show 95% credible intervals
  ggtitle("Posterior Distributions of Coefficients") +
  xlab("Estimate")

```

#### Hypothesis 2b: Exam path safety

It may be possible that participants in the counterfactual condition learn a more accurate model of the environment particularly where it matters. So we also predict that rational planning under beliefs obtained in the counterfactual condition will result in encountering fewer hazards than those obtained in the observation condition.

```{r}
fit.s2_hypothesis2b = world_df_s2 %>% 
  rename(environment = world_spec_id) %>% 
  mutate(condition = ifelse(condition == "counterfactual", 1, -1)) %>% 
  brm(
    formula = exam_trial_hazard_count ~ 1 + condition + (1 | game_id) + (1 | environment),
    family = Gamma(link = "log"),
    seed = 1,
    chains = 8,
    iter = 4000,
    cores = parallel::detectCores(),
    file = 'cache/fit.s2_hypothesis2b',
  )

summary(fit.s2_hypothesis2b)

fit.s2_hypothesis2b %>%
  emmeans(specs=pairwise~condition)

```

```{r}
posterior <- as_draws_df(fit.s2_hypothesis2b)
mcmc_areas(posterior, 
           pars = c("b_Intercept", "b_condition"),
           prob = 0.95) +  # Show 95% credible intervals
  ggtitle("Posterior Distributions of Coefficients") +
  xlab("Estimate")

```

# Plots

```{r}
recode_labels <- c("observation" = "experience", 
                   "hypothetical" = "experience + hypothetical",
                   "counterfactual" = "experience + counterfactual")

condition_labels <- c("experience" = "experience", 
                      "experience + hypothetical" = "hypothetical",
                      "experience + counterfactual" = "counterfactual")

condition_legend_labels <- c("experience" = "experience", 
                             "experience + hypothetical" = "+ hypothetical",
                             "experience + counterfactual" = "+ counterfactual")

day_split_labels <- c("split 1 of 3" = "split 1", 
                      "split 2 of 3" = "split 2", 
                      "split 3 of 3" = "split 3")

quicksand_df_s1 <- quicksand_df_s1 %>%
  mutate(condition = recode(condition, !!!recode_labels))
  # mutate(condition = recode(condition, !!!as.list(condition_labels)))

quicksand_df_s2 <- quicksand_df_s2 %>%
  mutate(condition = recode(condition, !!!recode_labels))

world_df_s2 <- world_df_s2 %>%
  mutate(condition = recode(condition, !!!recode_labels))
```

## Manipulation check: Simulated paths

```{r}
path_type_levels <- c("experience", "hypothetical", "counterfactual")

# Pilot Study: Manipulation Check
fig_s1_manipulation <- quicksand_df_s1 %>%
  filter(trial_type == "quicksand-simulate") %>%
  mutate(path_type = case_when(
      trial_type == "quicksand-simulate" & condition == "experience + hypothetical" ~ "hypothetical",
      trial_type == "quicksand-simulate" & condition == "experience + counterfactual" ~ "counterfactual",
      TRUE ~ "experience" # Force experience level
    ),
    path_type = factor(path_type, levels = path_type_levels)
  ) %>%
  ggplot(aes(x = path_type, 
             y = hazard_count, 
             fill = path_type)) +
  stat_summary(fun = mean, 
               geom = "bar", 
               color = "black") +
  stat_summary(fun.data = mean_cl_boot, 
               geom = "linerange", 
               size = 1,
               width = 0.2) +
  scale_fill_manual(values = trial_palette) +
  scale_y_continuous(breaks = seq(0, 5, 1), 
                     limit = c(0, 5),
                     expand = expansion(mult = 0.01)) +
  labs(title = "Study 1",
       x = "Path type",
       y = "Unsafe tiles in path",
       fill = "Path type")

# Full Study: Manipulation Check
fig_s2_manipulation <- quicksand_df_s2 %>%
  filter(condition == "experience + counterfactual") %>%
  mutate(trial_type = recode(trial_type, "navigation" = "experience")) %>%
  mutate(path_type = factor(trial_type, levels = path_type_levels)) %>%
  ggplot(aes(x = path_type, 
             y = hazard_count, 
             fill = path_type)) +
  stat_summary(fun = mean, 
               geom = "bar", 
               color = "black") +
  stat_summary(fun.data = mean_cl_boot, 
               geom = "linerange", 
               size = 1,
               width = 0.2) +
  scale_fill_manual(values = trial_palette,
                    breaks = path_type_levels,
                    drop = FALSE) +
  scale_y_continuous(breaks = seq(0, 5, 1), 
                     limit = c(0, 5),
                     expand = expansion(mult = 0.01)) +
  labs(title = "Study 2",
       y = " ",
       x = "Trial type",
       fill = "Path type") + 
  guides(fill = "none")

legend_plot <- ggplot(data.frame(path_type = path_type_levels), 
                      aes(x = path_type, fill = path_type)) +
  geom_bar() +  # Dummy plot to create legend
  scale_fill_manual(values = trial_palette, name = "Path type") +
  theme_minimal() + 
  theme(legend.position = "bottom") 

# Combine Plots in One Row
fig_combined_manipulation <- fig_s1_manipulation + fig_s2_manipulation +
  plot_layout(ncol = 2, guides = "collect") &
  plot_annotation(tag_levels = "A") & # uses plot.tag
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major.y = element_line(),
        legend.position = "bottom",
        legend.margin = margin(-10, 0, 0, 0))

ggsave(file.path(figures_dir, "manipulation_check.pdf"), width = 7, height = 3, useDingbats = FALSE)

fig_combined_manipulation

```

## Hypothesis 1: Navigation performance

```{r}
day_split_labels_new <- c("split 1 of 3" = "early", 
                          "split 2 of 3" = "middle", 
                          "split 3 of 3" = "late")

dodge_width <- position_dodge(width = 0.3)

condition_palette <- c("experience" = "#999999",
                       "random prior" = "#DBC7BD80",
                       "experience + counterfactual" = "#e41a1c",
                       "optimal learner" = "#63453680",
                       "experience + hypothetical" = "#377eb8",
                       "oracle" = "#3D2C2280")

condition_legend_labels <- c("experience", 
                             "random prior",
                             "+ counterfactual", 
                             "optimal learner", 
                             "+ hypothetical", 
                             "oracle")

model_df_s1_ <- model_df_s1 %>%
  left_join(quicksand_df_s1 %>% select(trial_id, day, days_binned), by = "trial_id")

model_df_s2_ <- model_df_s2 %>%
  left_join(quicksand_df_s2 %>% select(trial_id, day, days_binned), by = "trial_id")


combined_s1 <- quicksand_df_s1 %>%
  filter(trial_type == "quicksand-planner") %>%
  select(condition, day, days_binned, hazard_count) %>%
  mutate(source = "human")

combined_s1_model <- model_df_s1_ %>%
  select(condition, day, days_binned, hazard_count) %>%
  mutate(source = "model")

combined_s1_all <- bind_rows(combined_s1, combined_s1_model)  %>%
  mutate(condition = factor(condition, levels = c(
    "experience", 
    "random prior",
    "experience + counterfactual", 
    "optimal learner", 
    "experience + hypothetical", 
    "oracle"
  )))

combined_s2 <- quicksand_df_s2 %>%
  filter(trial_type == "navigation") %>%
  select(condition, day, days_binned, hazard_count) %>%
  mutate(source = "human")

combined_s2_model <- model_df_s2_ %>%
  select(condition, day, days_binned, hazard_count) %>%
  mutate(source = "model")

combined_s2_all <- bind_rows(combined_s2, combined_s2_model)  %>%
  mutate(condition = factor(condition, levels = c(
    "experience", 
    "random prior",
    "experience + counterfactual", 
    "optimal learner", 
    "experience + hypothetical", 
    "oracle"
  )))

fig_s1_hyp1 <- combined_s1_all %>%
  ggplot(aes(x = days_binned, y = hazard_count, color = condition, group = condition)) +
  stat_summary(fun = mean, geom = "point", size = 3, position = dodge_width) +
  stat_summary(fun.data = mean_cl_boot, geom = "linerange", width = 0.2, position = dodge_width) +
  stat_summary(fun = mean, geom = "line", position = dodge_width) +
  scale_color_manual(values = condition_palette, labels = condition_legend_labels) + 
  scale_x_discrete(labels = day_split_labels_new) +
  scale_y_continuous(breaks = seq(1.6, 4.0, 0.2), expand = expansion(mult = 0.01)) +
  coord_cartesian(ylim = c(1.6, 4.0)) +
  labs(title = "Study 1", x = "Trial order (binned)", y = "Unsafe tiles", color = "Condition") +
  guides(color = guide_legend(nrow = 2))  # allow 2 rows if legend gets crowded

fig_s2_hyp1 <- combined_s2_all %>%
  ggplot(aes(x = days_binned, y = hazard_count, color = condition, group = condition)) +
  stat_summary(fun = mean, geom = "point", size = 3, position = dodge_width) +
  stat_summary(fun.data = mean_cl_boot, geom = "linerange", width = 0.2, position = dodge_width) +
  stat_summary(fun = mean, geom = "line", position = dodge_width) +
  scale_color_manual(values = condition_palette, labels = condition_legend_labels) +
  scale_x_discrete(labels = day_split_labels_new) +
  scale_y_continuous(breaks = seq(1.6, 4.0, 0.2), expand = expansion(mult = 0.01)) +
  coord_cartesian(ylim = c(1.6, 4.0)) +
  labs(title = "Study 2", y = "", x = "Trial order (binned)") +
  guides(color = "none")


fig_combined <- fig_s1_hyp1 + fig_s2_hyp1 + 
  plot_layout(ncol = 2, guides = "collect") &
  plot_annotation(tag_levels = "A") &
  theme(axis.title.x = element_blank(),
        panel.grid.major.y = element_line(),
        legend.position = "bottom",
        legend.margin = margin(-10, 0, 0, 0))

ggsave(file.path(figures_dir, 'hypothesis1.pdf'), width = 7, height = 4, useDingbats = FALSE)

fig_combined
```

```{r}
fig_s1_hyp1 <- combined_s1_all %>%
  ggplot(aes(x = day, y = hazard_count, color = condition)) +
  geom_point(alpha = 0.3, position = dodge_width) +
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs"), se = TRUE) +
  scale_color_manual(values = condition_palette, labels = condition_legend_labels) + 
  scale_y_continuous(breaks = seq(1.0, 8.4, 0.2), expand = expansion(mult = 0.01)) +
  coord_cartesian(ylim = c(1.0, 5.4)) +
  labs(title = "Study 1", x = "Trial (day)", y = "Unsafe tiles", color = "Condition") +
  guides(color = guide_legend(nrow = 2))

fig_s2_hyp1 <- combined_s2_all %>%
  ggplot(aes(x = day, y = hazard_count, color = condition)) +
  geom_point(alpha = 0.3, position = dodge_width) +
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs"), se = TRUE) +
  scale_color_manual(values = condition_palette, labels = condition_legend_labels) +
  scale_y_continuous(breaks = seq(1.4, 4.5, 0.5), expand = expansion(mult = 0.01)) +
  coord_cartesian(ylim = c(1.4, 4.5)) +
  labs(title = "Study 2", y = "", x = "Trial (day)") +
  guides(color = "none")

fig_combined <- fig_s1_hyp1 + fig_s2_hyp1 + 
  plot_layout(ncol = 2, guides = "collect") &
  plot_annotation(tag_levels = "A") &
  theme(axis.title.x = element_blank(),
        panel.grid.major.y = element_line(),
        legend.position = "bottom",
        legend.margin = margin(-10, 0, 0, 0))

fig_combined

```


## Hypothesis 2: Exam performance

```{r fig.width = 7, fig.height = 3}
# Exam Correct Tiles
fig_exam_correct <- world_df_s2 %>%
  ggplot(aes(x = condition, 
             y = exam_trial_correct_tiles, 
             fill = condition)) +
  stat_summary(fun = mean, 
               geom = "bar", 
               color = "black") +
  stat_summary(fun.data = mean_cl_boot, 
               geom = "linerange", 
               size = 0.7,
               width = 0.2) +
  geom_point(size = 0.1,
             shape = 21,
             color = "gray25",
             position = position_jitter(height = 0.2, width = 0.2),
             show.legend = FALSE) + 
  scale_fill_manual(values = condition_palette,
                    labels = condition_legend_labels) +
  scale_x_discrete(labels = condition_labels) +
  scale_y_continuous(breaks = seq(0, 27, 5),
                     limits = c(0, 25),
                     expand = expansion(mult = 0.01)) +
  labs(title = NULL,
       x = "Condition",
       y = "Correct tiles",
       fill = "Condition") +
  guides(fill = guide_legend(nrow = 1))

# Exam Hazard Count (Rational planner unsafe tiles)
fig_exam_hazard <- world_df_s2 %>%
  ggplot(aes(x = condition, 
             y = exam_trial_hazard_count, 
             fill = condition)) +
  stat_summary(fun = mean, 
               geom = "bar", 
               color = "black") +
  stat_summary(fun.data = mean_cl_boot, 
               geom = "linerange", 
               size = 0.7,
               width = 0.2) +
  geom_point(size = 0.1,
             shape = 21,
             color = "gray25",
             position = position_jitter(height = 0, width = 0.2),
             show.legend = FALSE) + 
  scale_fill_manual(values = condition_palette,
                    labels = condition_legend_labels) +
  scale_x_discrete(labels = condition_labels) +
  scale_y_continuous(breaks = seq(0, 8, 1), 
                     expand = expansion(mult = 0.01)) +
  labs(title = NULL,
       x = "Condition",
       y = "Unsafe tiles",
       fill = "Condition") +
  guides(fill = guide_legend(nrow = 1))

# Combine both plots in one row
fig_combined <- fig_exam_correct + fig_exam_hazard + 
  plot_layout(ncol = 2, guides = "collect") & 
  plot_annotation(tag_levels = "A") &
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major.y = element_line(),
        legend.position = "bottom",
        legend.margin = margin(-10, 0, 0, 0)) 

ggsave(file.path(figures_dir, 'hypothesis2.pdf'), width = 7, height = 3, useDingbats = FALSE)
fig_combined
```
